---
output: github_document
---

# targetsketch

This R/Shiny app is a companion to the [`targets`](https://github.com/ropensci/targets) R package. It helps new users learn [`targets`](https://github.com/ropensci/targets), and it helps new and experienced users set up new [`targets`](https://github.com/ropensci/targets)-powered projects. Simply provide a [`_targets.R` script](https://books.ropensci.org/targets/walkthrough.html), and `targetsketch` will show you the end-to-end dependency graph of your workflow, a manifest of the pipeline, and produce a downloadable `_targets.R` script to get your project started.

# Access

This app is available online at [https://wlandau.shinyapps.io/targetsketch](https://wlandau.shinyapps.io/targetsketch). If you cannot access it, you can install it locally in an R session.

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("wlandau/targetsketch")
```

Then run it on your own machine.

```{r, eval = FALSE}
targetsketch::targetsketch()
```

# Usage

1. Navigate to the `Pipeline` view (left sidebar).
2. Write your [`_targets.R` script](https://books.ropensci.org/targets/walkthrough.html) in the `_targets.R` box. The code must return a valid list of [`tar_target()`](https://docs.ropensci.org/targets/reference/tar_target.html) objects at the end. If you want the app to analyze custom functions called in the commands of the targets, define them in the `_targets.R` box as well.  See the [`tar_script()`](https://docs.ropensci.org/targets/reference/tar_script.html) help file for more details.
4. Click `Update` button in the `Control` box.
5. If you want to download the code in the `_targets.R` box as an R script file, click the `Download` button in the `Control` box.

# Contributing

Contributions are welcome. If you plan to [file an issue](https://github.com/wlandau/targetsketch/issues/new/choose) or [submit a pull request](https://github.com/wlandau/targetsketch/pulls), please first read the [code of conduct](https://github.com/wlandau/targetsketch/blob/main/CODE_OF_CONDUCT.md) and [rules for contributing](https://github.com/wlandau/targetsketch/blob/main/CONTRIBUTING.md). 
